\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-10-18 k-planar.tex
created response.* and started doing the referee's revisions

For at least two applications, the planarity of $H$ in \cref{1_planar_product} is critical in obtaining asymptotically tight bounds \cite{BDJM,DFMS21}. \cref{1_planar_product} is proven in the more general setting of $d$-framed multigraphs, which also implies a product structure theorem for $d$-map graphs in which $H$ is a planar with treewidth 3.

>>>>

For at least two applications, the planarity of $H$ in \cref{1_planar_product} is critical in obtaining asymptotically tight bounds \cite{BDJM,DFMS21}. \cref{1_planar_product} is proven in the more general setting of $d$-framed multigraphs, which also implies a product structure theorem for $d$-map graphs in which $H$ is a planar graph with treewidth 3.
